%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2024 Yash Modi <yashnimeshmodi@gmail.com>
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to customize the page and not use a CV template fully
\documentclass[a4paper,10.5pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within the experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% plain numbered pages
\pagestyle{plain} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Yash Modi} \\[7pt]
\href{https://github.com/yashnmodi}{\raisebox{-0.05\height}\faGithub\ yashnmodi} \ $|$ \ 
\href{https://linkedin.com/in/yashnmodi}{\raisebox{-0.05\height}\faLinkedin\ yashnmodi} \ $|$ \ 
%\href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
\href{mailto:yashnimeshmodi@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ yashnimeshmodi@gmail.com} \ $|$ \ 
\href{tel:+917383112237}{\raisebox{-0.05\height}\faMobile \ +91 738-311-2237} \\
\end{tabularx}

\section{Professional Summary}
%This CV can also be automatically compiled and published using GitHub Actions. For details, \href{https://github.com/jitinnair1/autoCV}{click here}.
Accomplished Software Engineer with over \textbf{5 years} of expertise in application development. Specializes in technical analysis, design, development, and debugging. A proactive team player adept in development methodologies, data structures, algorithms, and multiple programming languages.

\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Backend Development & \normalsize{Java, Spring Boot, SQL, REST/SOAP, Android, Python(Familiar), Lua(Familiar), Shell, JUnit}\\
Frontend Development & \normalsize{HTML, CSS, Javascript}\\
Databases & \normalsize{Oracle SQL, MySQL, MSSQL, MongoDB, Redis}\\
Tools & \normalsize{Git, Maven, Jenkins, Docker, JIRA, Spinnaker, Graphana}\\
Soft Skills & \normalsize{Decisive team leader, Motivated team player, Bias for action, Deliver results, Ability to work under pressure}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\large{Pine Labs}} & \hfill Pune \\[3pt]
\textbf{Lead Engineer} & \hfill Jun 2024 - present \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Led the migration and transition of the newly acquired product, \href{https://www.pinelabs.com/blog/announcing-the-launch-of-pine-labs-next-gen-credit-issuing-platform-credit}{PineLabs Credit+} issuing. Coordinated closely with DEVOPS and Infrastructure-IT teams to set up the entire Credit+ Issuing application in the PineLabs environment within \textbf{2.5 months}. Enabled existing applications to run as \textbf{Docker} containerized applications on \textbf{Kubernetes}, leveraging \textbf{Jenkins} and \textbf{Spinnaker} for CI/CD.
        \item[--] Spearheaded the replacement of Oracle Argus, RSA SecurID, and HashiVault with \textbf{KeyCloak}, \textbf{PrivacyIDEA}, and \textbf{AWS KMS}, respectively. These changes significantly \textbf{reduced licensing costs} for the organization.
        \item[--] Addressed gaps in the encryption-decryption mechanism for inbound and outbound APIs, and implemented \textbf{payShield 10k HSM} commands to secure critical transactions.
        %Twilio integration, OLTP exposure, GFT, Dolphin scheduler%
        \item[--] Demonstrated exceptional leadership throughout the project lifecycle, from inception to execution, ensuring successful delivery within stipulated timelines.
    \end{itemize}
\end{minipage}}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Senior Software Engineer} & \hfill Dec 2022 - Jun 2024 \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Orchestrated the comprehensive overhaul of a Payout application, replacing \textbf{RabbitMQ} with \textbf{Redis} for data streams and channels which enabled self-healing mechanisms allowing the system to autonomously recover from disruptions. As part of the refactoring process, enhanced low-level designs and implemented design patterns such as \textbf{command}, \textbf{abstract factory}, and \textbf{thread-safe singleton}. These improvements significantly boosted the application's efficiency and reliability, facilitating seamless online transactions exceeding 300 crores within a single year.
        \item[--] Created a generic Java scheduler application to process reconciliation files received from multiple financial institutions and update the payout transaction transaction status in the database.
        \item[--] Skillfully utilized \textbf{Apache APISIX} API Gateway to consolidate and streamline diverse API solutions within the \href{https://developers.qwikcilver.com/}{Pine Labs Issuing Business suite}, resulting in a unified and efficient API infrastructure. Engineered a robust \textbf{Single Sign-On (SSO)} feature to provide seamless and secure access to these APIs, significantly simplifying the authentication process, enhancing system cohesion, and reducing overall complexity.
        \item[--] Developed a \textbf{Spring Boot} application from scratch to integrate with an API gateway, supporting custom API transformations according to \textbf{OpenAPI} specifications and enabling \textbf{API orchestration}.
        \item[--] Developed a payment checkout application from scratch featuring a redirection-based payment processor. Continuously integrated \textbf{multiple payment gateways} while providing seamless and standardized API-based integration to client systems, achieving a throughput of \textbf{450 TPS}. Implemented a \textbf{delay queue system} to periodically fetch transaction statuses until they reach a terminal state, and to store failed \textbf{webhook notifications} of transaction events for retry.
        \item[--] Collaborated with cross-functional teams including Information Security, Performance, and Quality Engineering. Resolved security vulnerabilities, including \textbf{OWASP Top 10} issues. Followed \textbf{Test Driven Development (TDD)} in building a large-scale application, significantly reducing the number of bugs. Utilized \textbf{concurrent hashmaps}, \textbf{KD tree algorithms}, and \textbf{Redis} to enhance application performance.
        \item[--] Pioneered the development of a \textbf{custom annotation} for data logging, significantly improving debugging and application monitoring processes. This streamlined approach enhances development efficiency and ensures robust application performance.
    \end{itemize}
\end{minipage}}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{\large{Tata Consultancy Services}} & \hfill Thane \\[3pt]
\textbf{Systems Engineer} & \hfill Jun 2019 - Dec 2022 \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Worked as a back-end developer in a banking application built on Spring, Apache Camel. Developed \textbf{REST APIs} from scratch. Had exposure to work with \textbf{SOAP APIs}, SOA services, Oracle DBMS, Web-server configurations, thread dumps and heap dumps.
        \item[--] Implemented security measures to comply with PCI-DSS and prevent \textbf{MITM and Replay attacks}. Code optimizations to improve concurrency and caching efficiency. Re-designed login mechanism to allow multi-user login from a single device.
        \item[--] Developed common components like audit logging, authentication, authorization and encryption. Also, configured CI/CD pipeline in \textbf{Jenkins} to automate the source code scanning and deployment.
    \end{itemize}
\end{minipage}}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Project Trainee} & \hfill Jan 2019 - Apr 2019 \\[3pt]
\multicolumn{2}{@{}X@{}}{Developed the document extractor tool from scratch which can extract relevant details from lengthy documents i.e. Rent Agreement, Affidavit using Python, Tesseract and MongoDB.}  \\
\end{tabularx}  

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
% \section{Projects}
% \begin{tabularx}{\linewidth}{ @{}l r@{} }
% \textbf{Inventory Management System} & \hfill \href{https://github.com/yashnmodi/Inventory_Management}{Link} \\
% \medskip
% \multicolumn{2}{@{}X@{}}{Developed RESTful web application from scratch using Spring Boot, Java8, MongoDB, JWT Authentication. State-less authentication with JWT. Applied filters for logging. Configured OTP service for generating, and validating OTPs.} \\
% \textbf{RestOMS: Restaurant Order Management System} & \hfill \href{https://github.com/yashnmodi/RestOMS}{Link} \\
% \medskip
% \multicolumn{2}{@{}X@{}}{Spring MVC-based web app. Used SpringBoot for bootstrapping and Mysql for Database. It has three components - customer portal for Menu \& Order, Kitchen for preparation and Admin for management and accounting.}  \\
% \textbf{ShareDroid: File sharing app} & \hfill \href{https://github.com/yashnmodi/ShareDroid}{Link} \\
% \multicolumn{2}{@{}X@{}}{Developed an Android app using P2P networking which facilitates rapid sharing of any file. The top speed achieved is 4.5 MBPS.}  \\
% \end{tabularx}

\section{Projects}
\href{https://github.com/yashnmodi/Inventory_Management}{\textbf{Inventory Management System}} \\
Developed RESTful web application from scratch using Spring Boot, Java8, MongoDB, JWT Authentication. State-less authentication with JWT. Applied filters for logging. Configured OTP service for generating, and validating OTPs. \\ \\
\href{https://github.com/yashnmodi/RestOMS}{\textbf{RestOMS: Restaurant Order Management System}} \\
Spring MVC-based web app. Used SpringBoot for bootstrapping and Mysql for Database. It has three components - customer portal for Menu \& Order, Kitchen for preparation and Admin for management and accounting. \\ \\
\href{https://github.com/yashnmodi/ShareDroid}{\textbf{ShareDroid: File sharing app}} \\
Developed an Android app using P2P networking which facilitates rapid sharing of any file. The top speed achieved is 4.5 MBPS.

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2015 - 2019 & BE in Computer Engineering at \textbf{Gujarat Techonlogical University} \hfill (CGPA: 8.69) \\
2013 - 2015 & Class 12th, Gujarat Higher Secondary Education Board \hfill (83.33 \%) \\
2012 - 2013 & Class 10th, Gujarat Secondary Education Board \hfill (91.16 \%) \\ 
\end{tabularx}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\section{Achievements}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
On the Spot Award & For making the entire source code and logging operations PCI-DSS compliant. (2022) \\
Special Initiative Award & Received this for automating the back-end deployment using Jenkins. (2021) \\
Applause for Team Award & For excellent performance of the team. (2021) \\
Special Initiative Award & For delivering solutions quickly. (2019) \\
TCS CodeVita & Cleared Round-2 of TCS CodeVita Season 7. (2018) \\
Best Yoga Practitioner & 2nd Runner Up for performing best yoga at University level. (2016) \\
%JNV district 2nd
%star of the workplace
\end{tabularx}

%----------------------------------------------------------------------------------------
%	INTERESTS
%----------------------------------------------------------------------------------------
\section{Interests}
\begin{tabularx}{\linewidth}{@{}X @{}X @{}X}	
Playing badminton, volleyball & Self-improvement & Exploring Places \\
Practising Yoga & Watching movies \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	COURSEWORK
%----------------------------------------------------------------------------------------
%\section{Certificates}
%\begin{tabularx}{\linewidth}{@{}l X@{}}	
%Microservices with Spring Boot & Learning Docker
%\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
\begin{refsection}[citations.bib]
\nocite{*}
\printbibliography[heading=none]
\end{refsection}

\vfill
\center{\footnotesize Last updated: \today}
        
\end{document}
